### 2011-07-31 doc/theses/vitasek/diplomka.tex
Thesis: in progress.

\subsection{Constructions Heuristics}
1
% TODO can I format things in nomenclature?
\nomenclature{CH}{Construction Heuristic} %TODO decide on how to format CH/IH

@@

>>>>

\begin{center}
  \includegraphics[width=\textwidth]{images/metaheuristic.eps}
\end{center}

\subsection{Constructions Heuristics}
% TODO can I format things in nomenclature?
\nomenclature{CH}{Construction Heuristic} %TODO decide on how to format CH/IH

@@

The pseudocode is listed (cited from \cite{fidax} with trivial modifications) in \ref{ch-fidax}.

\begin{algorithm}
\caption{FIDAX CH}
\label{ch-fidax}
\begin{algorithmic}
\REQUIRE $C$ list of candidate AMs
\STATE $C' \gets C$ sorted by decreasing size
\STATE Compute the weight $w(m)$ of each $m$ in $C$
\FORALL{$t$ in $\Sigma^E$}
  \STATE Let $m$ be a \textbf{highest-weight} mapping of type $t$ in $C'$
  \STATE Remove from $C'$ all mappings of type $t$ except $m$
\ENDFOR
\FORALL{$m$ in $C'$}
  \STATE $S \gets$ all mappings in $C$ whose images intersect $\iota(m)$
  \IF{$w(m) > \sum_{p \in S} w(p)$}
    \STATE remove all $p \in S$ from $C'$
  \ELSE
  	\STATE remove $m$ from $C'$
  \ENDIF
\ENDFOR
\RETURN $C'$
\end{algorithmic}
\end{algorithm}
